A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-29 vignette/Manuscript2Word.Rmd
Add Lua author information

---
title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
   word_document:
      reference_docx: "Manuscript2Word_Template.docx"
bibliography: "../Mungbean.bib"
biblio-style: apalike
link-citations: yes
---

>>>>

---
title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
author:
  - Paul Melloy:
      email: Paul.Melloy@usq.edu.au
      institute: USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Adam H. Sparks:
      institute: USQ
institute:
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
   word_document:
      reference_docx: "Manuscript2Word_Template.docx"
      pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: "../Mungbean.bib"
biblio-style: apalike
link-citations: yes
---
